---
title: "Numerical Measures"
author: Carolusian <https://github.com/carolusian>
date: Sep 28, 2017
output: html_notebook
---

## Explain different numerical measures

### Quartile: 1st (lower), 2nd (median), 3rd (upper) quartiles

When the data is sorted in ascending order, quartiles are the values that cut of the first 25%, 50% and 70% of the data

```{r}
library(dplyr)
length(mtcars$mpg)
mpg <- sort(mtcars$mpg)

# calculate cut off positions
pos <- c(0, 0.25, 0.5, 0.75, 0.1) * 32 + 1
pos

# calculate the quartiles manually
first_quartile <- mpg[9]
second_quartile <- mpg[17]  
third_quartile <- mpg[25]

c(first_quartile, second_quartile, third_quartile)

# use `quantile` function which sorts the data for you as well
quantile(mtcars$mpg)
sort(mtcars$mpg) %>% 
  quantile()
```

### Percentile

n^th^ percentile of an observation varible is the value cut off the first n percent of the data when it is sorted. Quartile is a special form of percentile.

```{r}
quantile(mtcars$mpg, c(.15, .25, .50, .75, .85))
```

### Interquartile range

* It is the different of the upper quartile and the lower quartile; 
* It measures how far apart the middle portion of data spreads.

```{r}
lower_quartile <- quantile(mtcars$mpg)[[2]]
upper_quartile <- quantile(mtcars$mpg)[[4]]

# calculate manually
upper_quartile - lower_quartile
IQR(mtcars$mpg) == upper_quartile - lower_quartile
```

### Box plot

Box plot is a graphical representation of quartiles

```{r}
library(ggplot2)
ggplot(mtcars, aes(x=factor(0), mpg)) +
  geom_boxplot()
```

### Variance & Standard Deviation 

```{r}
```